Study protocol

### 2021-05-05 Manuscript/Protocol.Rmd
feat: better pkg loader function

# Store the file
dir.create(file.path('Annotations', 'Session1'))
folder <- file.path('Annotations', 'Session1')
dir.create(folder, recursive = T)
file <- file.path(folder, paste0('Records_', safe_now(), '.xlsx'))
WriteXLS::WriteXLS(records, ExcelFileName = file)
```

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	save_annotation_file(reorder_query = query, session_name = 'Session1') 
```

>>>>

This annotation file needs to be stored in an **Annotation Session** folder which will contain all annotation information. This operation is streamlined by the `create_session()`, which also help manage duplicated sessions.

```{r managing records, echo = TRUE, eval = FALSE}
create_session(Annotation_data, session_name = 'Session1')
```

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	save_annotation_file(reorder_query = query) %>%  
	# Create a new session with the records
	create_session(session_name = 'Session1')
```
